
---
######Example Code Final Project
#Original code file
---

# -------------------------------------------------------------------------
####1a: Uploading all the sheets
```{r}
library(readxl)
library(dplyr)
library(magrittr)
library(knitr)
file_path <- '/Users/'
T0_list <- list()
sheet_names <- c('SABD0000000003, Ch 2', 'SABD0000000003, Ch 3', 'SABD0000000003, Ch 4',
                 'SABD0000000003, Ch 5', 'SABD0000000003, Ch 6', 'SABD0000000003, Ch 7',
                 'SABD0000000003, Ch 8', 'SABD0000000003, Ch 9', 'SABD0000000003, Ch 10')

for (sheet_name in sheet_names) {
  df <- read_excel(file_path, sheet = sheet_name)
  T0_list[[sheet_name]] <- df
}
for (i in 1:length(sheet_names)) {
  assign(paste0("ch", i + 1), T0_list[[sheet_names[i]]], envir = .GlobalEnv)
}
```

# -------------------------------------------------------------------------
####2a: Renaming the third column
```{r}
T0_list <- list(ch2, ch3, ch4, ch5, ch6, ch7, ch8, ch9, ch10)
for (i in 1:length(T0_list)) {
  names(T0_list[[i]])[3] <- "Delta_Time"
}
T0_list
```

# -------------------------------------------------------------------------
####3a: Adding in another column for the different channels
```{r}
for (i in 1:length(T0_list)) {
  channel_name <- paste0("channel_", i + 1)
  T0_list[[i]]$Channel <- as.factor(channel_name)
}
```

# -------------------------------------------------------------------------
####4a: Merging all the data sheets together into one dataframe
```{r}
combined_df <- T0_list[[1]]
for (i in 2:length(T0_list)) {
  combined_df <- merge(combined_df, T0_list[[i]], all = TRUE)
}
```

# -------------------------------------------------------------------------
####5a: Showing only selected columns of data
```{r}
selected_columns <- combined_df %>%
  select(Delta_Time, Oxygen, Temperature, Channel)

```

# -------------------------------------------------------------------------
####6a: Plotting at entire time interval
```{r}
library(dplyr)
start_time <- 0.0
end_time <- 61
selected_data <- selected_columns[selected_columns$Delta_Time >= start_time & selected_columns$Delta_Time <= end_time, ]
selected_data <- na.omit(selected_data)

library(ggplot2)
ggplot(selected_data, aes(x = Delta_Time, y = Oxygen, color = Channel)) +
  geom_point() +
  labs(title = "T0 Run X Oxygen vs. Time (Full Time)",
       x = "Time (Minutes)",
       y = "Oxygen") +
  theme_minimal()
```

# -------------------------------------------------------------------------
####7a: Choosing data based on specific time range (5-15 Minutes) 
##Double check with graph of full run time to see if we need to use 10-20
```{r}
library(dplyr)
start_time <- 5.0
end_time <- 15.0
selected_data <- selected_columns[selected_columns$Delta_Time >= start_time & selected_columns$Delta_Time <= end_time, ]
selected_data <- na.omit(selected_data)

library(ggplot2)
ggplot(selected_data, aes(x = Delta_Time, y = Oxygen, color = Channel, group = Channel)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  labs(title = "T0 Run X Oxygen vs. Time 5-15 Minutes",
       x = "Time (Minutes)",
       y = "Oxygen") +
  theme_minimal()
```

# -------------------------------------------------------------------------
####8a: Making a table for the slopes and finding the slope difference
####Also adding in the intercept, avg temps
```{r}
lm_models <- lapply(split(selected_data, selected_data$Channel), function(sub_data) {
  model <- lm(Oxygen ~ Delta_Time, data = sub_data)
  coefficients <- coef(model)
  data.frame(
    Channel = unique(sub_data$Channel),
    Slope = coefficients[2],
    Intercept = coefficients[1]
  )
})

slope_table_light <- do.call(rbind, lm_models)

slope_channel_5 <- slope_table_light$Slope[slope_table_light$Channel == "channel_5"]
intercept_channel_5 <- slope_table_light$Intercept[slope_table_light$Channel == "channel_5"]

slope_table_light$Light_Slope_Difference <- slope_table_light$Slope - slope_channel_5


Light_average_temp <- selected_data %>%
  group_by(Channel) %>%
  summarize(Light_Avg_Temperature = mean(Temperature, na.rm = TRUE))

Light_average_temp

slope_table_light <- merge(slope_table_light, Light_average_temp, by = "Channel", all.x = TRUE)

print(slope_table_light)

```
# ----------------------------------------------------------------------------------------------------------------------------
####1b: Repeat for dark runs
```{r}
library(readxl)
file_path <- '/Users/'
T0_list <- list()
sheet_names <- c('SABD0000000003, Ch 2', 'SABD0000000003, Ch 3', 'SABD0000000003, Ch 4',
                 'SABD0000000003, Ch 5', 'SABD0000000003, Ch 6', 'SABD0000000003, Ch 7',
                 'SABD0000000003, Ch 8', 'SABD0000000003, Ch 9', 'SABD0000000003, Ch 10')

for (sheet_name in sheet_names) {
  df <- read_excel(file_path, sheet = sheet_name)
  T0_list[[sheet_name]] <- df
}
for (i in 1:length(sheet_names)) {
  assign(paste0("ch", i + 1), T0_list[[sheet_names[i]]], envir = .GlobalEnv)
}
```

# -------------------------------------------------------------------------
####2b: Renaming the third column
```{r}
T0_list <- list(ch2, ch3, ch4, ch5, ch6, ch7, ch8, ch9, ch10)
for (i in 1:length(T0_list)) {
  names(T0_list[[i]])[3] <- "Delta_Time"
}
T0_list
```

# -------------------------------------------------------------------------
####3b: Adding in another column for the different channels
```{r}
for (i in 1:length(T0_list)) {
  channel_name <- paste0("channel_", i + 1)
  T0_list[[i]]$Channel <- as.factor(channel_name)
}
```

# -------------------------------------------------------------------------
####4b: Merging all the data sheets together into one dataframe
```{r}
combined_df <- T0_list[[1]]
for (i in 2:length(T0_list)) {
  combined_df <- merge(combined_df, T0_list[[i]], all = TRUE)
}
```

# -------------------------------------------------------------------------
####5b: Showing only selected columns of data
```{r}
selected_columns <- combined_df %>%
  select(Delta_Time, Oxygen, Temperature, Channel)
```

# -------------------------------------------------------------------------
####6b: Plotting at entire time interval
```{r}
library(dplyr)
start_time <- 0.0
end_time <- 61
selected_data <- selected_columns[selected_columns$Delta_Time >= start_time & selected_columns$Delta_Time <= end_time, ]
selected_data <- na.omit(selected_data)

library(ggplot2)
ggplot(selected_data, aes(x = Delta_Time, y = Oxygen, color = Channel)) +
  geom_point() +
  labs(title = "T0 Run X Oxygen vs. Time (Full Time)",
       x = "Time (Minutes)",
       y = "Oxygen") +
  theme_minimal()
```

# -------------------------------------------------------------------------
####7b: Choosing data based on specific time range (5-15 Minutes) 
##Double check with graph of full run time to see if we need to use 10-20
```{r}
library(dplyr)
start_time <- 5.0
end_time <- 15.0
selected_data <- selected_columns[selected_columns$Delta_Time >= start_time & selected_columns$Delta_Time <= end_time, ]
selected_data <- na.omit(selected_data)

library(ggplot2)
ggplot(selected_data, aes(x = Delta_Time, y = Oxygen, color = Channel, group = Channel)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  labs(title = "T0 Run X Oxygen vs. Time 5-15 Minutes",
       x = "Time (Minutes)",
       y = "Oxygen") +
  theme_minimal()
```

# -------------------------------------------------------------------------
####8b: Making a table for the slopes and finding the slope difference
####Also adding in the intercept
```{r}
lm_models <- lapply(split(selected_data, selected_data$Channel), function(sub_data) {
  model <- lm(Oxygen ~ Delta_Time, data = sub_data)
  coefficients <- coef(model)
  data.frame(
    Channel = unique(sub_data$Channel),
    Slope = coefficients[2],
    Intercept = coefficients[1]
  )
})

slope_table_dark <- do.call(rbind, lm_models)

# Calculate the slope and intercept differences
slope_channel_5 <- slope_table_dark$Slope[slope_table_dark$Channel == "channel_5"]
intercept_channel_5 <- slope_table_dark$Intercept[slope_table_dark$Channel == "channel_5"]

slope_table_dark$Dark_Slope_Difference <- slope_table_dark$Slope - slope_channel_5

Dark_average_temp <- selected_data %>%
  group_by(Channel) %>%
  summarize(Dark_Avg_Temperature = mean(Temperature, na.rm = TRUE))

Dark_average_temp

slope_table_dark <- merge(slope_table_dark, Dark_average_temp, by = "Channel", all.x = TRUE)

print(slope_table_dark)

```
# -------------------------------------------------------------------------------------------------------------------------------
####9: Merging the two slope tables together & Light slope diff - Dark slope diff = Net Environmental Production (NEP)
```{r}
merged_slope_table <- merge(slope_table_light, slope_table_dark, by = "Channel", suffixes = c("_Light", "_Dark"))

merged_slope_table$NEP <- merged_slope_table$Light_Slope_Difference - merged_slope_table$Dark_Slope_Difference

merged_slope_table <- merged_slope_table %>%
  arrange(as.numeric(gsub("channel_", "", Channel)))

print(merged_slope_table)

```
# -------------------------------------------------------------------------
####10: adding in a frag ID column to correspond with channel name
##Must change for each run---this one is M.cap for T0
```{r}
library(readxl)
library(dplyr)

excel_file_path <- '/Users/'

sheet_name <- 'Run1'
frag_ids <- read_excel(excel_file_path, sheet = sheet_name)

frag_ids <- frag_ids[, c("Channel", "Frag_ID")]

merged_slope_table <- merge(merged_slope_table, frag_ids, by = "Channel", all.x = TRUE)

merged_slope_table <- merged_slope_table %>%
  arrange(as.numeric(gsub("channel_", "", Channel)))

print(merged_slope_table)

```
# -------------------------------------------------------------------------
####11:Exporting the final table
```{r}
write.csv(merged_slope_table, file = '/Users/', row.names = FALSE)
```

