### Question 0

*  Draw a concepts diagram that uses all the following Github terminology 
   * Include any missing keywords that will simplify the concepts diagrams 


`Push`, `Repository`, `Clone`, `Pull`, `Pull Request`, `Branch`, `Merging`, `Github Client`, `README file`, `Private or Public`

```{r}
# Add your photo here
# https://docs.google.com/document/d/1mFiZMhJSAWX7i6w1vTpAmrs8N5Bcr1LwswpRVI_EvEQ/edit?usp=sharing
```

#### Question 1

`matrix(c(1,2,3,4,5,6) , nrow = 3)`

* Running the expression produces the following matrix

|  |  |
|---|---|
| 1 | 4 |
| 2 | 5 |
| 3 | 6 |

* How can you modify the call to `matrix()` to produce the following matrix instead?

|   | col_1 |  col_2 |
| --- |---|---|
| row_1 | 1 | 2 |
| row_2 | 3 | 4 |
| row_3 | 5 | 6 |

* Note that you need to name the columns (col_1 and col_2) and name the rows (row_1, row_2, row_3)

Hint: Use the `?` symbol to invoke the matrix documentation

```{r}
# Add your code here
my_matrix <- matrix (c(1,2,3,4,5,6) , byrow = "true" , nrow = 3)
rownames(my_matrix) <- c("row_1", "row_2", "row_3")
colnames(my_matrix) <- c("col_1", "col_2")
#my matrix doesn't show up below but will pull up in the global environment after running the code and in a new tab
```

#### Question 2

* Load then sort the airquality data frame on its `Temp` and `Solar.R` columns in reverse order (largest to smallest values)
  * The function to sort a data frame is called order
* Display only the first 15 lines of your table

```{r}
# Write your answer here
data("airquality")
head(airquality)
rev_solar_temp <- airquality[order(-airquality$Temp, -airquality$Solar.R), ]
head(rev_solar_temp, n = 15)
rev_solar_temp
```
#### Question 3

* Sort the airquality data frame on its `Temp` in decreasing order and `Solar.R` in increasing order
* Display only the first 15 lines of your table

```{r}
# Write your answer here
data("airquality")
head(airquality)
inc_solar_temp <- airquality[order(airquality$Solar.R, -airquality$Temp), ]
head(inc_solar_temp, n = 15)
inc_solar_temp
```
#### Question 4

* There are various ways to select a subset of observations from a data frame.

* Consult your [R Reference Card](https://cran.r-project.org/doc/contrib/Baggott-refcard-v2.pdf), see `Data Selection and Manipulation` section.
  * What operations can you use to select all observations where the temperature is 72. Give at least two different answers to this question


```{r}
# Write your answer here
#first subset method
temp_subset <- subset(airquality, Temp == 72,)
temp_subset
```


```{r}
#another possible subset method
temp_subset_b <- which(airquality$Temp == 72)
temp_subset_b
#im not sure if this is all the information that I would need, not sure how to show the table like with subset, but it gives the corresponding row numbers

```

#### Question 6

* You may have noticed when working with the `airqulity` data that some values show as `NA`
 * `NA` stands for not available, or missing values.
* A major part of data wrangling consists of cleaning missing values by either:
  * Dropping the lines that have missing values
   * Sometimes we can drop the column with missing values if the column is made of predominantly missing values
  * Imputing the missing values, which uses educated guesses (or more complex algorithms) to fill the missing values
  
* Find and remove all rows that are missing values for the `Solar.R` or `Ozone` variables
* Save the cleaned data to a new data frame called airquality_no_na
  * How many lines have been removed?

```{r}
# Write your answer here
airquality_nona <- na.omit(airquality)
#42 observations have been removed, full table found in global environment
```

#### Question 7
* Let's use a different strategy and impute the missing value.
  * replace the missing values for Solar.R using that month's average.
  * Example:
    * The missing value for line 6 should be replaced with the average for month 5.
    * The missing value for line 97 should be replaced with the average for month 8.

```{r}
# Write your answer here
#finding monthly means (may and aug)
may_subset <- subset(airquality, Month == 5, "Solar.R")
may_no_na <- na.omit(may_subset)
May_mean <- mean(may_no_na$Solar.R)

aug_subset <- subset(airquality, Month == 8, "Solar.R")
aug_no_na <- na.omit(aug_subset)
Aug_mean <- mean(aug_no_na$Solar.R)
```


```{r}
#subbing in the means found above
may_subset[is.na(may_subset)] <- May_mean
aug_subset[is.na(aug_subset)] <- Aug_mean

#showing the new data frames
may_subset
aug_subset
```

