##Amanda & Lauryn

### Q0: Sampling and Distribution

You are studying the population of a specific type of marine algae in different locations. Assume the algal density is normally distributed. You take samples from two locations (Location A and Location B) to compare the algae populations. Generate synthetic data to represent the algal density (individuals per square meter) at these two locations. Assume a mean density of 200 and 220 individuals/m^2 with a common standard deviation of 20 individuals/m^2 for both locations, with 50 samples from each location.


```{r}
### Write your code here
mean_loca <- 200
mean_locb <- 220
sd <-20
sample_size <- 50

algaldensity_loca <- rnorm(sample_size, mean_loca, sd)
algaldensity_locb <- rnorm(sample_size, mean_locb, sd)

algaldensity_loca
algaldensity_locb

algalDensity <- c(algaldensity_loca, algaldensity_locb)
locations <- rep(c("1","2"), each = sample_size)

dfLoc <- data.frame(Location = locations, algal_density = algalDensity)
head(dfLoc)
```

### Q1: Data Cleaning

Check your dataset for any outliers. 


```{r}
boxplot(algalDensity ~ Location, data = dfLoc, main = "Algal Density", 
        xlab = "Location", ylab = "Algal Density")

outliers_A <- boxplot.stats(algaldensity_loca)$out
outliers_B <- boxplot.stats(algaldensity_locb)$out

points(rep(1, length(outliers_A)), outliers_A)
points(rep(2, length(outliers_B)), outliers_B)

q1 <- quantile(dfLoc$algalDensity, 0.25)
q3 <- quantile(dfLoc$algalDensity, 0.75)
iqr <- q3 - q1
lower_fence <- q1 - 1.5 * iqr
upper_fence <- q3 + 1.5 * iqr


summary(algalDensity)
```


### Q2: Visualization and Kernel Density Estimation (KDE)

Plot a Kernel Density Estimation (geom_density plot) to visualize the distribution of algal densities at both locations. 


```{r}
### Write your code here
library(ggplot2)

ggplot(dfLoc, aes(x = algalDensity, fill = locations))+
  geom_density(alpha = 0.5) +
  labs(title = "Algal Density Estimation", x = "Algal Density", y = "Density") 
```

### Q3: Binomial Distribution
Suppose in a new survey, at each location, you take 10 random samples and in each sample, you identify whether a particular species of marine algae is present or not. Assume the probability of finding this species in a sample is 0.7 at Location A and 0.5 at Location B.

Simulate this scenario using a binomial distribution, and compare the probability of finding the species in at least 7 out of 10 samples at both locations.

```{r}
### Write your code here
prob_A <- 0.7
prob_B <- 0.5
sample_size <- 10

prob_species_A <- dbinom(7:10, size = sample_size, prob = prob_A)
prob_species_B <- dbinom(7:10, size = sample_size, prob = prob_B)

prob7_A <- sum(prob_species_A)
prob7_B <- sum(prob_species_B)

prob7_A
prob7_B

```

### Q4: Poisson Distribution
Imagine a scenario where you are studying the occurrences of a particular rare marine event, such as the sighting of a rare marine species, over a set period at a specified location. Assume the average rate of occurrence is 3 per month.

Utilize a Poisson distribution to calculate the probability of observing exactly 5 occurrences in a month, and the probability of observing 3 or fewer occurrences in a month.

```{r}
### Write your code here
avg_rate <- 3
obs_events <- 5

prob_Occur <- dpois(obs_events, lambda = avg_rate)
prob_Occur

obs_eventsb <-3
prob_Occur2 <- ppois(obs_eventsb, lambda = avg_rate)
prob_Occur2

```

### Q5: 
consider the following two lists. 

```{r}
list1 <- c(44.40, 47.70, 65.59, 50.71, 51.29, 67.15, 54.61, 37.35, 43.13, 45.54, 62.24, 53.60, 54.01, 51.11, 
           44.44, 67.87, 54.98, 30.33, 57.01, 45.27, 39.32, 47.82, 39.74, 42.71, 43.75, 33.13, 58.38, 51.53, 
           38.62, 62.54, 54.26, 47.05, 58.95, 58.78, 58.22, 56.89, 55.54, 49.38, 46.94, 46.20, 43.05, 47.92, 
           37.35, 71.69, 62.08, 38.77, 45.97, 45.33, 57.80, 49.17, 52.53, 49.71, 49.57, 63.69, 47.74, 65.16, 
           34.51, 55.85, 51.24, 52.16, 53.80, 44.98, 46.67, 39.81, 39.28, 53.04, 54.48, 50.53, 59.22, 70.50, 
           45.09, 26.91, 60.06, 42.91, 43.12, 60.26, 47.15, 37.79, 51.81, 48.61, 50.06, 53.85, 46.29, 56.44, 
           47.80, 53.32, 60.97, 54.35, 46.74, 61.49, 59.94, 55.48, 52.39, 43.72, 63.61, 44.00, 71.87, 65.33, 
           47.64, 39.74)

list2 <- c(44.34, 48.85, 41.30, 39.79, 30.73, 44.32, 33.23, 19.98, 39.30, 58.78, 36.37, 54.12, 20.73, 44.17, 
           52.79, 49.52, 46.59, 35.39, 32.25, 29.64, 46.76, 30.79, 37.64, 41.16, 72.66, 35.22, 48.53, 46.17, 
           30.57, 43.93, 66.67, 51.77, 45.62, 38.66, 14.20, 61.97, 23.09, 56.10, 73.64, 23.34, 55.53, 41.07, 
           21.42, 22.28, 20.98, 37.04, 23.07, 55.32, 76.50, 25.69, 56.82, 56.54, 49.98, 29.87, 43.21, 40.79, 
           53.44, 39.41, 59.65, 39.38, 60.79, 29.26, 26.10, 93.62, 38.75, 49.47, 54.55, 37.74, 52.75, 50.53, 
           41.77, 45.98, 44.49, 76.93, 33.88, 28.56, 45.57, 49.66, 51.55, 38.12, 29.05, 63.95, 39.76, 32.02, 
           41.46, 42.04, 61.65, 46.27, 56.31, 37.51, 48.22, 40.13, 46.42, 31.57, 25.34, 74.96, 54.01, 26.23, 
           35.83, 27.22)

```

These list were generated using the following code

set.seed(123)  # Setting a seed for reproducibility
list1 <- round(rnorm(100, mean = 50, sd = 10), 2)  # Generating 100 values from a normal distribution
list2 <- round(rnorm(100, mean = 45, sd = 15), 2)  # Generating 100 values from another normal distribution


Compare the distributions of these two lists to determine if they originate from the same distribution or from different distributions.

1. Use geom_density to create a density plot for each list on the same graph. Use different colors to distinguish between the two lists:
```{r}
### Write your code here
list1 <- round(rnorm(100, mean = 50, sd = 10), 2)  
list2 <- round(rnorm(100, mean = 45, sd = 15), 2)
library(ggplot2)


data <- data.frame(
  Value = c(list1, list2),
  Group = rep(c("List 1", "List 2"), each = 100)
)


ggplot(data, aes(x = Value, fill = Group)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density Plot Comparison", x = "Value", y = "Density") 

```

Examine the plot you have generated. Do you think list1 and list2 come from the same distribution or different distributions? Why?
Write down your observations and reasoning.


* Write your answer below
They would be from different distributions because their maximums are different, the wideness of the peaks are different and the shape of the curves are also noticeably different. 
